Observation of the Torsional Motion of a Solar Jet at the Limb

### 2016-08-18 paper/ms_temp_paper.tex
temperature analysis

\cref{fig:}

>>>>

\cref{fig:temp-slit} demonstrates the behavioural change of the temperature across the normal of the feature by slit based analysis.
By performing this analysis over the time domain of the second ejection of plasma material, we will acertain whether the feature has any impact on the atmosphere.
The difficulty with this form if measurement is that the feature itself is not particularly wide, $~1$ Mm, and therefore is has only one or two pixels of actual jet material for us to examine.
The jet is located around the $3rd$ and $4th$ pixels of the x axis, and as we would expect we see a moderate dip, when compared to the surroundings. 
Noticeable as well, however, is that at what is approximatley the boundaries, there is a peak in temperature, before it drops as distance increases with respect to the jet.

These values are not conclusive, we require temperature maps on a much finer spatial scale, and as well, new techniques to develop to overcome the problems of the extremely broad H$\alpha$ and He II lines causing a blurring of possible values.
However, in conjunction with the observations presented here of possible shearing or Kelvin Helmholtz instability causing a lack of emission at the boundary of the jet, we can present the hypothesis more confidently.
In terms of the bigger picture in which spicules/jets/macrospicules contribute to heating of the solar corona, the results produced by this feature are not typical.
With respect to other studies, this feature cannot be considered that quick, or large, or excessively rotational, yet it may be having a measurable effect.
Hence, applying this kind of comprehensive analysis to multiple jets, particularly rapidly evolving examples, to ascertain their impact on the atmosphere fully is the next area of investigation for these jets.
An endeavour which will be aided significantly by the operation commencement of DKIST, with its superior everything.
